11 A company buys 100 lightbulbs, each of which has an exponential lifetime of
1000 hours. What is the expected time for the first of these bulbs to burn
out? (See Exercise 10.)

$lambda$ = $$\frac {1} {1000} $$

100 x $$\frac {1} {1000} $$ = $$\frac {1} {10} $$

```{r}
x <- 1/(100*1/1000)
print(paste("the expected time for the first bulb to burn out is ",x))
```


14 Assume that X1 and X2 are independent random variables, each having an
exponential density with parameter λ. Show that Z = X1 − X2 has density
fZ(z) = (1/2)λe−λ|z|

f(x$~1~$) = $lambda$ e$^-$lambda$ $ x$~1~$ 
f(x$~2~$) = $lambda$ e$^-$lambda$ $ x$~2~$ 

f(x$~1~$) x f(x$~2~$) = $lambda$ $^2$e$^ -$lambda$ (x$~1~$ + x$~2~$)$

x$~1~$ = z+ x$~2~$

f(z + x$~2~$) = $lambda$ $^2$e$^-$lambda$ (z + 2x$~2~$)$

f$~z~$(z) = $$\frac {1} {2} $$ $lambda$ e$^$lambda$|z|$

1 Let X be a continuous random variable with mean µ = 10 and variance
σ
2 = 100/3. Using Chebyshev’s Inequality, find an upper bound for the
following probabilities.
P(|X- $mu$| $\ge$ k$sigma$ $\le$ 1/k$^2$

(a) P(|X − 10| ≥ 2).
```{r}
x = 1/(2*sqrt(3)/10)**2
print(paste(" x = ",x," however the bound is 1"))
```

(b) P(|X − 10| ≥ 5).
```{r}
y = 1/(sqrt(3)/2)**2
print(paste("probability is ",y," however the bound is 1"))
```

(c) P(|X − 10| ≥ 9).
```{r}
 w = 1/(9*sqrt(3)/10)**2
print(paste("probability is ",w))
```

(d) P(|X − 10| ≥ 20).

```{r}
v = 1/(2*sqrt(3))**2
print(paste("probability is ",v))

```

