---
title: "Schwenker-assign 10"
author: "Anne Schwenker"
date: "March 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars.
A guard agrees to make a series of bets with him. If Smith bets A dollars,
he wins A dollars with probability .4 and loses A dollars with probability .6.
Find the probability that he wins 8 dollars before losing all of his money if
(a) he bets 1 dollar each time (timid strategy).
qz = (q/p)$^z$ − 1/(q/p)$^M$ − 1
```{r}
x=(1.5^1-1)/(1.5^8-1)
print(x)
```


(b) he bets, each time, as much as possible but not more than necessary to
bring his fortune up to 8 dollars (bold strategy).
in order to reach $8 he would need to win three times in a row if he is betting all his money -- 1,2,4,8
```{r}
y = dbinom(3,3,0.4)
print(y)


```

(c) Which strategy gives Smith the better chance of getting out of jail?

the bold stragegy gives him the better chance of getting out of jail 