---
title: "Schwenker_assignment_12"
author: "Anne Schwenker"
date: "November 11, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
why <- read.csv(url('https://raw.githubusercontent.com/aschwenker/Fall2019/master/who.csv'))
head(why)
```
 Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the
variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss
whether the assumptions of simple linear regression met.
```{r}
plot(why$TotExp,  why$LifeExp, main='scatterplot', ylab='Life Expentancy', xlab = 'Total Expenditure', col=3)

```
```{r}
lm = lm(why$LifeExp~why$TotExp)
lm
summary(lm)
```
Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss
whether the assumptions of simple linear regression met.

R^2:
0.2577, Adjusted R-squared: 0.2537 - low, model only explains 25% of the response variable 

F-statistic:
65.26 on 1 and 188 DF, high
p-value: 7.714e-14 - near 0, reject the null hypothesis 

Residual standard error: 9.371 on 188 degrees of freedom 
```{r}
mean(lm$residuals)
plot(lm)
```


assumptions of simple linear regression :
1. linearity - these variables do not show a linear relationship
2. Homoscedasticity - from the plot of the model we can see the variables are not randomly distributed
3. Autocorrelation of residuals:
```{r}
lmtest::dwtest(lm)
```

2. Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06
power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r
re-run the simple regression model using the transformed variables. Provide and interpret the F
statistics, R^2, standard error, and p-values. Which model is "better?"

```{r}
#Raise LifeExp to the 4.6 power & TotExp to the 0.06 power
LifeExp_46 <- why$LifeExp^4.6
TotExp_06 <- why$TotExp^0.06
plot(TotExp_06,  LifeExp_46, main='scatterplot', ylab='Life Expentancy ^4.6', xlab = 'Total Expenditure ^ 0.06', col=3)

#Linear regression model
LM_2 <- lm(LifeExp_46 ~ TotExp_06)
summary(LM_2)
```
Provide and interpret the F
statistics, R^2, standard error, and p-values. Which model is "better?"


R^2:
0.7298, Adjusted R-squared: 0.7283 - model explains about 73% of the response variable 

F-statistic:
507.7 on 1 and 188 DF, large

p-value: 2.2e-16 - near 0, reject the null hypothesis 

Residual standard error: 90490000 on 188 degrees of freedom - higher

```{r}
mean(LM_2$residuals)
plot(LM_2)
```
assumptions of simple linear regression :
1. linearity - these variables do show a linear relationship
2. Homoscedasticity - from the plot of the model we can see the variables are randomly distributed
3. Autocorrelation of residuals:
```{r}
lmtest::dwtest(LM_2)
```
The second model is a better based on meeting the simple linear regression assumptions and having better R^2


3. Using the results from 3, forecast life expectancy when TotExp^.06 =1.5. Then forecast life
expectancy when TotExp^.06=2.5.

```{r}
range <- data.frame(TotExp_06 = c(1.5,2.5))
predict(LM_2, range,interval="predict")^(1/4.6)
```

4. Build the following multiple regression model and interpret the F Statistics, R^2, standard error,
and p-values. How good is the model?
LifeExp = b0+b1 x PropMd + b2 x TotExp +b3 x PropMD x TotExp

```{r}
plot(LifeExp ~ PropMD + TotExp + TotExp:PropMD, why)
LM_3 <- lm(LifeExp ~ PropMD + TotExp + TotExp:PropMD, why)
summary(LM_3)
```
R^2:
0.3574, Adjusted R-squared: 0.3471 - model explains about 35% of the response variable 

F-statistic:
34.49 on 3 and 186 DF

p-value: 2.2e-16 - near 0, reject the null hypothesis 

Residual standard error: 8.765 on 186 degrees of freedom

This model does not meet the assumptions, and is therefore no good
```{r}
mean(LM_3$residuals)
plot(LM_3)
```
assumptions of simple linear regression :
1. linearity - these variables do not show a linear relationship
2. Homoscedasticity - from the plot of the model we can see the variables are not randomly distributed
3. Autocorrelation of residuals:
```{r}
lmtest::dwtest(LM_3)
```

5. Forecast LifeExp when PropMD=.03 and TotExp = 14. Does this forecast seem realistic? Why
or why not?

```{r}
Prediction <- data.frame(PropMD=0.03, TotExp=14)
predict(LM_3, Prediction,interval="predict")
```

No this is not realistic, the fit being 107.696 shows this model does not work