---
title: "Schwenker assign7"
author: "Anne Schwenker"
date: "March 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi’s. Find the distribution of Y .
 P(Y=x)  $$\frac {(k−x+1)^n−(k−x)^n} {k^n} $$

2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).
This machine has a manufacturer’s expected lifetime of 10 years. This means
that we expect one failure every ten years. (Include the probability statements
and R Code for each part.).
a. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a geometric. (Hint: the probability is
equivalent to not failing during the first 8 years..)
```{r}
p_fail <-1/10
not_fail<- 1-p_fail
pp<-pgeom(8, p_fail, lower.tail = TRUE, log.p = FALSE)
print(paste("probability using geometric modeling is ",pp))

expected_value<-1/p_fail
print(paste("expected value using geometric modeling is ",expected_value))

sd<-sqrt(not_fail/p_fail**2)
print(paste("standard deviation using geometric modeling is ",sd))

```


b. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as an exponential.
```{r}
prob_exp <-1-pexp(8,0.1)
print(paste("probability using exponential modeling is ",prob_exp))
exp_expected<-1/(1/10)
print(paste("expected value using exponential modeling is ",exp_expected))

exp_sd <-sqrt((1)/(.1^2))
print(paste("standard deviation using exponential modeling is ",exp_sd))

```

c. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8
years)

```{r}
p_fail <-1/10
not_fail<- 1-p_fail
p_binom<-pbinom(0,8,p_fail)
print(paste("probability using binomial modeling is ",p_binom))
binom_expected_value<-8*p_fail
print(paste("expected value using binomial modeling is ",binom_expected_value))

binom_sd<-sqrt(8*p_fail*not_fail)
print(paste("standard deviation using binomial modeling is ",binom_sd))

```

d. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a Poisson. 
```{r}
lambda <- 8*p_fail/1
print(paste("lambda is ",lambda))
p_pois<-ppois(0,lambda)
print(paste("probability using poisson modeling is ",p_pois))

pois_expected <- lambda
print(paste("expected value using poisson modeling is ",pois_expected))

pois_sd<-sqrt(lambda)
print(paste("standard deviation using poisson modeling is ",pois_sd))

```

