---
title: "ASchwenker_Assignment_3"
author: "Anne Schwenker"
date: "February 16, 2019"
output: html_document
---
1. Problem set 1
(1) What is the rank of the matrix A?
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(matrixcalc)
library(pracma)
A <-matrix(c(1,-1,0,5,2,0,1,4,3,1,-2,-2,4,3,1,-3),nrow=4,ncol=4)
print("Matrix A defined as :")
A
print("echelon form of matrix A is :")
rref(A)
print("all rows are independent, so")
print("rank of matrix A is:")

matrix.rank(A)
```


(2) Given an mxn matrix where m > n, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?
maximum rank is m
minimum rank is 1
(3) What is the rank of matrix B?
```{r echo=FALSE}
B <-matrix(c(1,3,2,2,6,4,1,3,2),nrow=3,ncol=3)
print("Matrix B defined as :")
B
print("echelon form of matrix B is :")
rref(B)
print("only 1 row of B is independent, so")
print("rank of matrix B is:")

matrix.rank(B)
```
2. Problem set 2
Compute the eigenvalues and eigenvectors of the matrix A. You’ll need to show your
work. You’ll need to write out the characteristic polynomial and show your solution.


-$\lambda^3$+ 11$\lambda^2$-34$\lambda$+24
```{r}
A <-matrix(c(1,0,0,2,4,0,3,5,6),nrow=3,ncol=3)
print("Matrix A defined as :")
A
e<-eigen(A)
print("Eigenvalues are")
ev<-e$values
ev
print("eigenvector is")
v<-e$vectors
v
```

Please show your work using an R-markdown document. Please name your assignment
submission with your first initial and last name.
