---
title: "Schwenker-assign_4"
author: "Anne Schwenker"
date: "February 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Problem Set 1
In this problem, we’ll verify using R that SVD and Eigenvalues are related as worked
out in the weekly module. Given a 3 × 2 matrix A
```{r}
A<-matrix(c(1,-1,2,0,3,4),nrow=2,ncol=3)
A
```

(1)
write code in R to compute X = AA$^T$ and Y = A$^T$A. Then, compute the eigenvalues
and eigenvectors of X and Y using the built-in commans in R.
Then, compute the left-singular, singular values, and right-singular vectors of A using
the svd command. Examine the two sets of singular vectors and show that they are indeed
eigenvectors of X and Y. In addition, the two non-zero eigenvalues (the 3rd value will
be very close to zero, if not zero) of both X and Y are the same and are squares of the
non-zero singular values of A.
Your code should compute all these vectors and scalars and store them in variables.
Please add enough comments in your code to show me how to interpret your steps.
```{r}
X<-A%*%t(A)
Y<-t(A)%*%A
X
Y
eX<-eigen(X)
print(paste("eigen values of X are, "))
eigen_val_X <-eX$values
eigen_val_X

print("eigen vectors of X are")
eigen_vec_X <-eX$vectors
eigen_vec_X

eY<-eigen(Y)
print(paste("eigen values of Y are, "))
eigen_val_Y <-eY$values
eigen_val_Y

print("eigen vectors of Y are")
eigen_vec_Y <-eY$vectors
eigen_vec_Y

A_svd<-svd(A, nu=2,nv = 3)

print("left singular vectors of A are")
left_sing_A <- A_svd$u
left_sing_A
print("singular values of A are")
Sing_val_A<- A_svd$d
Sing_val_A
print("right singular vectors of A are")
Right_Sing_A<- A_svd$v
Right_Sing_A
all.equal(left_sing_A,eigen_vec_X )
#are not the same, because of negatives
print("taking the absolute value to remove negatives and show similarity")
eigen_vec_X_abs <- abs(eigen_vec_X)
eigen_vec_X_abs
left_sing_A_abs <- abs(left_sing_A)
left_sing_A_abs
print("when absolute values are compared")
all.equal(eigen_vec_X_abs,left_sing_A_abs)

Right_Sing_A
eigen_vec_Y
all.equal(Right_Sing_A,eigen_vec_Y )
print("taking the absolute value to remove negatives and show similarity")
#are not the same, because of negatives
eigen_vec_Y_abs <- abs(eigen_vec_Y)
eigen_vec_Y_abs
right_sing_A_abs <- abs(Right_Sing_A)
right_sing_A_abs
print("when absolute values are compared")
all.equal(eigen_vec_Y_abs,right_sing_A_abs)

```

2. Problem Set 2
Using the procedure outlined in section 1 of the weekly handout, write a function to
compute the inverse of a well-conditioned full-rank square matrix using co-factors. In order
to compute the co-factors, you may use built-in commands to compute the determinant.
Your function should have the following signature:
B = myinverse(A)
where A is a matrix and B is its inverse and A×B = I. The off-diagonal elements of I
should be close to zero, if not zero. Likewise, the diagonal elements should be close to 1, if
not 1. Small numerical precision errors are acceptable but the function myinverse should
be correct and must use co-factors and determinant of A to compute the inverse.

```{r}
library(QZ)
library(matrixcalc)
library(generalCorr)

conjugate_matrix <- function(A) {
  n <- nrow(A)
  B <- matrix(NA, n, n)
  for( i in 1:n )
    for( j in 1:n )
      B[i,j] <- cofactor(A, i, j)
  return(B)
}

myinverse <- function(A){ if(!is.singular.matrix(A) && is.square.matrix(A)){
  C<- conjugate_matrix(A)
  A_inv<-t(C)/det(A)
  return(A_inv)
}else{print(" matrix was either not square or could not get an inverse")}}
#run
funct_outcome <- myinverse(A)
#set sample matrix
A<-matrix(c(1,1,2,1),nrow=2,ncol=2)
A
#test agaist R package
built_in_outcome <-solve(A)
funct_outcome
built_in_outcome
#test for equality
all.equal(funct_outcome,built_in_outcome)
```

