---
title: "Schwenker Assignment 13"
author: "Anne Schwenker"
date: "November 23, 2019"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
(
$$\int x4e^{-7x} dx$$
u = -7x
du/dx = d/dx(-7x) = -7
du = -7dx
= $$ \int 4e^{-7x} dx = \int -1/7(-7)4e^{-7x} dx$$
= $$-1/7 \int x4e^{-7x} (-7dx) = \int -1/7(-7)4e^udu$$
$$-4/7 \int e^udu = -(4/7)e^u + c $$
replace u with -7x
-(4/7)e^{-7x} + c


Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of
dN/dt = 3150/t^4 -220 bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a
function N( t ) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.

$$ N′(t)=dn/dt=\int(−3150t4−220)dt$$
$$N(t) = 1050/t^3 - 220t + c$$
$$N(t)=1050/t^3 − 220t + C$$
$$N(1)= 1050 − 220 + C = 6530$$
C = 5700
$$N(t) = 1050/ t^3 − 220t + 5700$$
3. Find the total area of the red rectangles in the figure below, where the equation of the line is f ( x ) = 2x  9.

$$Area=\int 8.54.5(2x−9) dx$$
Area=(8.52−9(8.5)+C)−(4.52−9(4.5)+C)=16

4. Find the area of the region bounded by the graphs of the given equations.
y=x2−2x−2,y=x+2

x+2=x2−2x−20=x2−3x−40=(x−4)(x+1)
$$\int_{−1}^{4}(x+2)−(x2−2x−2)dx$$
$$ \int_{-1}^{4}(−x2+3x+4)dx$$
$−x^3/3+3x^2/2+4x|4−1
(−4^3/3+3(4)^2/2+4(4))−(− −1^3/3+3(−1)^2/2+4(−1))=20.83333

5. A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year. There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.
Without knowing the sales rate, 1 order will always be the lowest cost. If it were know who long it takes to sell a flat iron once it comes in, then daily storage rates could be calculated
```{r}
OrderYCostAll=vector()
Orders = vector()
for (i in 1:110){
  x=i
YCostStorage = 3.75*(x*(110/x))
YOrderCost = 8.25*(x)
OrderYCost = YCostStorage+YOrderCost
Orders = c(OrderYCostAll,x)
OrderYCostAll=c(OrderYCostAll,OrderYCost)}

print(paste("number of orders",1,"costs ",min(OrderYCostAll)))
```

$$\int ln(9x)*(x^6)dx$$
u=9x , du/dx = 1/x
$$dv/dx = x^6 , v =\int x^6 dx = 1/7 x^7$$
$$\int u \frac{dv}{dx}dx = uv- \int v \frac{du}{dv}dx$$ 
$$\int ln(9x) x^6 dx= \frac{1}{7} x^6 dx$$
$$\frac{7}{49}x^7 ln(9x)-\frac{1}{49} x^7 +c$$
$$\frac{1}{49}(7ln(9x)-1)+c$$

Determine whether f(x) is a probability density function on the interval 
$$[1,e^6] If not, determine the value of the definite integral.$$
$$f(x)= \frac {1}{6}$$
$$\int_{e^6}{1} \frac{1}{6x}dx = \frac{1}{6}ln(x)|{e^6}{1}$$
$$\frac{1}{6}ln(e^6)-\frac{1}{6}ln(1)=1$$
