---
title: "assignment 2"
author: "Anne Schwenker"
date: "February 6, 2019"
output: html_document
---
1. Problem set 1
(1) Show that $A^T$A $\neq$ A$A^T$
```{r}
A<-matrix(c(0,1,0,0),nrow = 2, ncol = 2)
A
At<-t(A)
AtA<-At%*%A
AAt<-A%*%At
AtA
AAt
identical(AtA, AAt) 
```

in general. (Proof and demonstration.)
(2) For a special type of square matrix A, we get $A^T$A = A$A^T$
Under what conditions could this be true? (Hint: The Identity matrix I is an example of such a matrix).

If the matrix is symmetical, its transpose will be identical, thus $A^T$A = A$A^T$

```{r}
A<-matrix(c(3,0,0,3),nrow = 2, ncol = 2)
A
At<-t(A)
AtA<-At%*%A
AAt<-A%*%At
AtA
AAt
identical(AtA, AAt)
```

2. Problem set 2
Matrix factorization is a very important problem. There are supercomputers built just
to do matrix factorizations. Every second you are on an airplane, matrices are being
factorized. Radars that track flights use a technique called Kalman filtering. At the heart
of Kalman Filtering is a Matrix Factorization operation. Kalman Filters are solving linear
systems of equations when they track your flight using radars.
Write an R function to factorize a square matrix A into LU or LDU, whichever you
prefer. 
```{r}
library(matrixcalc)
LUD_3 <- function(A){
  a1<-A[1,1]
  b1<-A[2,1]
  b2<-A[2,2]
  c1<-A[3,1]
  c2<-A[3,2]
  multiplier_1<- -1*b1/a1
  multiplier_2 <- -1*c1/a1
  
  # create L based on matrix to fill in lower with multipliers
  R1<- A[1,]
  R2<-A[2,]
  R3<- A[3,]
  U<-R1
  U2<-((R1*multiplier_1)+R2)
  print(U2)
  U3_<-((R1*multiplier_2)+R3)
  U3_b2<-U2[2]
  U3_c2<-U3_[2]

  multiplier_3 <- -1*(U3_c2/U3_b2)
  print((multiplier_3))

  print(((U2*multiplier_3)))
  U3<-((U2*multiplier_3)+U3_)
  U<-rbind(U,U2,U3)
  print(U)
  L<-matrix(c(1,-1*multiplier_1,-1*multiplier_2,0,1,-1*multiplier_3,0,0,1),nrow=3,ncol=3)
  print(L)
  luA <- lu.decomposition( A )
  L2 <- luA$L
  U2 <- luA$U
  identical(U, U2)
  identical(L, L2)
}

A<-matrix(c(1,-2,3,4,8,4,-3,5,7),nrow = 3, ncol = 3)
LUD_3(A)

```
